Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-09-11 Ben_Manuscripts/structure_paper/Draft.tex
Merge branch 'master' of github.com:shirtsgroup/LLC_Membranes

  More highly selective nanoporous membranes would be extremely useful in order
  to perform complex aqueous separations with seawater and various sources of
  wastewater. Sodium chloride and boron in seawater \cite{fritzmann_state---art_2007}, and organic micropollutants
  found in municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} are examples of the
  diverse constituents of various water sources. By efficiently
  separating contaminants from feed solutions with highly selective membranes,
  one can reduce the number of required membrane passes and post-treatment steps
  needed for a given filtration process \cite{werber_materials_2016}, thus lowering energy requirements.
  Additionally, one can extract valuable resources from the feed streams. For
  example, flowback water produced during hydraulic fracturing of shale
  formations contains dissolved species such as acetate whose extraction could be
  economically valuable \cite{dischinger_application_2017}.

@@

 % (2) existing nanoporous membranes + drawbacks

  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
  filtration processes that can be used to separate solutes on the order of 1 nm
  in size and smaller, as well as ions, however the porous architecture of
  commercially dominant membranes lack uniformity which severely impacts their
  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their fabrication involves the spontaneous
  assembly of polymers into disordered structures which offer separation pathways
  that are tortuous and polydisperse in size \cite{werber_materials_2016}.
  Tortuosity increases the effective length that a solute must travel, while
  polydispersity limits membrane selectivity.

  % (3) justification for why nanostructured membranes are a good idea for this
  % long-term route towards highly selective membranes are those that are nanostructured
  Nanostructured porous membrane materials have become increasingly popular for
  aqueous separations applications because they offer the ability to control pore
  architecture at the molecular scale, thereby permitting the design of
  solute-specific separation membranes \cite{humplik_nanostructured_2011},
  however their development has been limited by the ability to synthesize and
  scale various fundamentally sound technologies. Graphene sheets are atomically
  thick which results in excellent water permeability but defects during
  manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
  Molecular dynamics (MD) simulations of carbon nanotubes show promise
  \cite{humplik_nanostructured_2011}, but synthetic techniques are unable to
  achieve scalable alignment and pore monodispersity
  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Consequently, there is a
  need for a scalable nanostructured porous membrane.

>>>>

  More highly selective nanoporous membranes would be extremely useful in order
  to perform complex aqueous separations with seawater and various sources of
  wastewater. Sodium chloride and boron in seawater
  \cite{fritzmann_state---art_2007}, and organic micropollutants found in
  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} are
  examples of the diverse constituents of these water sources. By efficiently
  separating contaminants from feed solutions with highly selective membranes,
  it is is possibl to reduce the number of required membrane passes and post-treatment steps
  needed for a given filtration process \cite{werber_materials_2016}, thus
  lowering energy requirements. Additionally, one can extract valuable resources
  from the feed streams. For example, flowback water produced during hydraulic
  fracturing of shale formations contains dissolved species such as acetate whose
  extraction has economic value \cite{dischinger_application_2017}.

@@

 % BJC14: (2) existing nanoporous membranes + drawbacks

  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
  filtration processes that can be used to separate solutes on the order of 1 nm
  in size and smaller, as well as ions. However the porous architecture of
  commercially 
  %MRS15: may be too strong an assertion.
  %dominant
  available 
  membranes lack uniformity which severely impacts their
  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
  fabrication involves the spontaneous assembly of polymers into disordered
  structures which offer separation pathways that are tortuous and polydisperse
  in size \cite{werber_materials_2016}. Tortuosity increases the effective
  length that a solute must travel, while polydispersity limits membrane
  selectivity.

  % BJC14: (3) justification for why nanostructured membranes are a good idea for this
  % long-term route towards highly selective membranes are those that are nanostructured
  %MRS15: popilar for separations applications would imply the are getting a larger market share now, 
  %though my impression is that they are research topics of heavy interest, but not yet that commercially viable.  Check my chainge below.
  Nanostructured porous membrane materials have become 
  %increasingly popular
  an increasingly popular research area for
  aqueous separations applications because they offer the ability to control pore
  architecture at the molecular scale, thereby permitting the design of
  solute-specific separation membranes \cite{humplik_nanostructured_2011}.
  However their development has been limited by the ability to synthesize and
  scale 
  %MRS15: not sure what you mean by ``fundamentally sound technologies''. THat the underlying principles are good, but that scaling is hard? Fundamentally sound seems to suggest that both principles and scaling are good, but that's not what the implication is.
  various fundamentally sound technologies. Graphene sheets are atomically
  thick which results in excellent water permeability but defects during
  manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
  Molecular dynamics (MD) simulations of carbon nanotubes show promise
  \cite{humplik_nanostructured_2011}, but synthetic techniques are unable to
  achieve scalable alignment and pore monodispersity
  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Consequently, there is a
  need for a scalable nanostructured porous membrane.
